Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-05-06 paper.tex
editing Section 4

However, we assume a simplified and stationary model for magnetic
fields and turbulence. We do not account for the time-varying energy
density in compressible waves, which are thought to be necessary for
the acceleration process \citep{brunetti07,brunetti11}, as the cluster
merger proceeds.  So our approach is orthogonal (and complementary) to
e.g., simulations of \citealp{2015ApJ...800...60M} that focus on the
time-dependent compressible turbulence while adopting a simplified
treatment of CR that does not follow the transport of the CR
distribution function. Our approach of parametrizing turbulence
enables us to vary parameters associated with the unknown continuation
of magneto-hydrodynamical turbulence below the MHD scale and the
overall amplitude of compressible waves (that can in principle vary
depending on the details of a particular cluster merger).

@@

In this section we show that our three models individually reproduce
the observed Coma radio halo without violating gamma-ray bounds. The
level of emission is mainly driven by how efficient the CRs are
reaccelerated and for how long. After turbulent reacceleration, the
volume-weighted, relative CRp energy density and relative CRp number
density inside the RH for \Mflatturb (\Mstream), are found to be 2 (3)
\% and $2\times10^{-8}$ ($5\times10^{-8}$), respectively. As we will
see later, these densities are just of the right order of magnitude to
reproduce radio observations in the Coma cluster. We exploit the large
uncertainty in the turbulent profile and adjust $\alpha_\rmn{tu}$ for
each model so that the CRs have the correct spatial profile to match
the radio emission. The shape of the spectrum for each of model is
more complicated and is determined both from reacceleration and as
well as the gains and losses during the formation of the cluster. It
depends only weakly on the specifics of the CR injection at the shocks
(where the Mach number distribution of the shocks is the most
important quantity). The normalization of the spectrum is mainly
determined from the maximum acceleration efficiency (together with the
uncertain parameters $X_\rmn{tu}$, $\tau_\rmn{cl}$, and $k_0$). Given
the freedom in the turbulence, it might not be surprising that we match
the radio profile in Coma. Although, matching the spectrum without
violating gamma-ray bounds for each of our three models is more
surprising and is not a consequence of parameter fitting. We believe
that it is ultimately a consequence of the adopted physics and hint
that reacceleration is a viable explanation for giant radio
halos. Below we discuss in more detail the different emission
components of Coma.

\subsection{Modelling diffusive shock acceleration}
\label{sec:cosmo_sim}
In this paper we focus on our simulated cluster, g72a, which is a
massive $1.6\times10^{15}\,M_\odot$ cluster that experienced a merger
about 1 to 2 Gyrs ago \citep{2009MNRAS.399..497D}. Since the cluster
mass, density and temperature profiles are all similar to the well
studied Coma cluster \citep{2007MNRAS.378..385P,pinzke10}, we will
compare our calculations to radio and gamma-ray observations of Coma.

We use a simple test-particle model for the CR acceleration and
injection, where each shock injects CRs that trace a power-law in
momentum,
\begin{equation}
  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
\end{equation}
determined by the normalization $C(t)$ and the spectral index
$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
$\mathcal{M}$. It is given by the ratio of the upstream velocity
($u_2$) and the sound speed ($c_s$). The CR number density and CR
energy density are derived from
\begin{eqnarray}
n_\rmn{p} &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
\eps_\rmn{p} &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
\end{eqnarray}
where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
particle with momentum $p$. We adopt a fit to Monte Carlo simulations
of the thermal leakage process that relates the momentum of injected
protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
shocked plasma \citep{kang11}:
\begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{u_2}{p_{\rmn{th}}\,c} \left(1+
  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
\end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which we will later see corresponds to a conservative maximum energy
acceleration efficiency for protons of $10\%$. To derive the
acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see ][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{p,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\eps_\rmn{p,lin} =
  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
  \,\frac{\eps_\p}{n_\p}
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.

@@

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency \citep[see][for more
  discussion]{pinzke13}. However, as recent PIC simulations have
shown, this is likely very different at weak shocks, with electrons
efficiently accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. Some observations of radio relics suggest high values of
$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
CRes as a viable alternative scenario to secondary CRes as seeds for
the giant RHs. In our {\em M-primaries} scenario, the injected
distribution of CRes is derived in the same way as for the CRps. Once
they have been accelerated to relativistic energies, injected
electrons and protons are indistinguishable. We therefore assume that
CRp and CRe have the same distribution function $f_\rmn{e}(p) =
K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
  viable for primarily perpendicular
  shocks][]{2014ApJ...794..153G}. While this appears to contradict the
radial bias of magnetic fields in the bulk of the ICM as suggested by
observations \citep{2010NatPh...6..520P} and cluster simulations
\citep{2011ApJ...740...81R}, it does not necessarily apply to the
accretion shock regions, which show a field geometry with a net
perpendicular bias with respect to the shock normal---at least for
giant radio relics \citep{2010Sci...330..347V}.

@@

%%% moved from before

@@

In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\eps_\rmn{turb} \propto
\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization).

Note that in previous work on the Coma cluster, $\eps_\rmn{turb}
\propto \eps_\rmn{th}$ was adopted which roughly corresponds to
$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
different distributions for seed CRes constitute the main differences
compared to our work. Our flatter turbulent profiles are motivated by
fits to cosmological simulations
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
and the range indicates uncertainties of the turbulent profile in
Coma. Future observations (by Astro-H) and simulations will help to
clarify this issue.

@@

%%%

In Fig.~\ref{fig:sync_profile}, we find that all three scenarios in
which the seeds undergo Fermi-II reacceleration can reproduce the Coma
RH profile at 352~MHz. \AP{It is also clear that without turbulent
  reacceleration, the simulated radio profiles are too steep.} In the
panel {\it Brunetti et al. (2012)} we show that without CR streaming
or a flat turbulent profile, our simulations of reaccelerated CRs
produce radio profiles that are too steep. Indeed, even using the
assumptions of previous work -- where complete freedom in the seed
population was allowed -- it is not possible to reproduce observations
in both frequencies in any model. Note that decreasing acceleration
efficiency with radius does not change this conclusion much because of
the weak radial dependence of $D_\rmn{pp}(R)\propto
\eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}\sqrt{T(R)}$. This signals that
the problem is generic and requires either additional modifications to
the plasma physics of acceleration or a better understanding of
potential observational systematics. In addition there are differences
in the simulated density and temperature profiles in comparison to the
observed profile in Coma that impact the CR abundance as well as
cooling and reacceleration.

In principle, reacceleration via TTD leads to spectral steepening with
particle energy due to the inefficiency of the acceleration process to
counter the stronger cooling losses with increasing energy. Since
synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
spectral steepening of the radio spectrum (see \AP{the left panel of
  Fig.~\ref{fig:sync_spectrum}} where the continuous injection of
secondary CRes is absent). A given radio window samples higher energy
electrons for a decreasing field strength in the cluster
outskirts. Hence, the spectral steepening with energy should translate
into a radial spectral steepening \citep{brunetti12}. However, because
of the weak dependence of the electron Lorentz factor on emission
frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
importantly, our simulated fluid elements at a given radius sample a
broad distribution of shock history, density and temperature, which
implies very similar synchrotron brightness profiles at
$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
and simulated 1.4 GHz profiles could instead be due to systematic flux
calibration error in single dish observations. These could arise, for
instance, due to errors in point source subtraction. Interestingly, we
can match the 1.4 GHz data if we reduce the zero point by adding 10\%
of the central flux to every data point; this flattens the outer
profile\footnote{Lawrence Rudnick, private communication.}.
Alternatively, this may point to weaknesses in the theoretical
modeling of the particle acceleration process and may require a
stronger cutoff in the particle energy spectrum.

\subsection{Radio spectrum}
\label{sect:radio_spec}
In Fig.~\ref{fig:sync_spectrum} we show that our three models that
include Fermi-II reacceleration can individually reproduce the
convexly curved total radio spectrum found in the Coma cluster. Seed
CRs in \Mstream and \Mflatturb that do not experience turbulent
reacceleration have a power-law spectrum in disagreement with
observations. In order to match both the spatial and spectral profiles
in Coma, we adopt an acceleration efficiency for the strongest shocks
in our three models \Mprimary, \Mstream, and \Mflatturb to
$\zeta_{\rmn{e}} <0.003$, $\zeta_{\rmn{p}} < 0.1$, and
$\zeta_{\rmn{p}}<0.03$, respectively. Following the Mach number
($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
\cite{pinzke13}, the efficiency in weak shocks ($\mathcal{M}\sim
2.5-3.5$) that dominates the CR distribution function, has an
acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
and for electrons $\zeta_{\rmn{e}}\sim 0.001$. Interestingly, we find
that the radio luminosity from clusters in the OFF-state (DSA only)
and ON-state (DSA and reacceleration) differ by about a factor 10-20
in all our three models. \AP{This means that the secondary CRes are
  dominated by the reaccelerated fossil CRes and not from the CRes
  produced by reaccelerated CRps. However, for high frequencies
  ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is more
  efficient than reacceleration, the emission is dominated by the CRes
  produced in the continuous injection of electrons from reaccelerated
  CRps. It is also worth mentioning that the radio emission from
  secondary CRes are smoothly distributed around the cluster because
  of the continuous injection, hence the it is not dominated by
  outliers.} However, \sout{note that} for \Mprimary, the primary CRes
that generate most of the radio emission from the cluster in the
OFF-state are dominated by only a small fraction of the CRes. These
electrons are injected very recently and have not had time to cool
yet. Hence we expect there to be a large variance in the OFF-state of
different simulated clusters. As mentioned in
section~\ref{sect:param_comp}, combining radio observations with
gamma-ray limits allows us to put a lower limit to $X_\rmn{tu}$.  If
$X_\rmn{tu}$ is smaller than in our adopted models (where we assume
$X_\rmn{tu}=0.2$), then the efficiency of DSA has to be larger than
$\zeta_\rmn{p}\sim 0.1$ for the secondary CRes to reproduce the radio
observations. However, since the turbulent reacceleration acts on both
the secondary CRes and the CRps, while $\zeta_\rmn{p}$ only affects
the CRps, \Mstream and \Mflatturb would produce too much
gamma-rays. Hence we conclude that $X_\rmn{tu}\gtrsim0.2$ if all other
parameters are kept fixed. Although, we caution the reader to take
this limit too stringent because of the uncertainty in $k_0$ and
$\tau_\rmn{cl}$ that impact $X_\rmn{tu}$ for a fixed
$\tau_\rmn{D}$. This parameter space needs to be explored further in
future work in order to put more stringent limits on the level of
turbulence in clusters using radio and gamma-ray observations in
combination with turbulent reaccelerated CRs.

@@

How could we distinguish the different possibilities of a dominating
primary or secondary seed population of electrons observationally?
\AP{I do not understand the next scentence, could you clarify?} One
possibility that is relative insensitive to adopted parameters in our
models is to use high-frequency radio observations (with e.g., the
Jansky Very Large Array) where turbulent reacceleration (which has a
high energy cutoff) is no longer efficient (see
Fig.~\ref{fig:sync_spectrum}). The negative flux bowl of the
Sunyaev-Zel'dovich effect introduces a cutoff of the RH spectrum at
frequencies above $\gtrsim 10$~GHz \citep[][ depending on cluster mass
  and redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
subdominant \sout{hadronic} radio emission \AP{from freshly injected
  secondary CRes} may only be detectable in steep spectrum radio
sources \citep{2008Natur.455..944B}, which exhibit a cutoff at lower
radio frequencies and are thought to represent dying RHs as a result
of the decaying turbulence after a merger. Alternatively, one could
attempt to reconstruct the intrinsic high-frequency RH spectrum by
filling in the missing flux due to the Sunyaev-Zel'dovich effect by
precise measurements of the Compton-$y$ parameter at microwave
frequencies. Another possibility would consist in stacking the radio
data of radio-quiet clusters that do not exhibit RH emission
\AP{individually} \citep{2011ApJ...740L..28B}. This may reveal the
glow of radio emission due to steady state secondary
population. Emission from faint secondary electrons should still be
visible, whereas due to the much more intermittent nature of DSA
injection, primary CRe will instead show a sharp cutoff due to
cooling, and will not be visible at high energies (see
Fig.~\ref{fig:sync_spectrum}). \AP{Finally we want to mention that in
  the near future we hope to gain valuable information about the
  turbulent profile in galaxy clusters from the recently launched
  X-ray satellite ASTRO-H. Alternatively, as magnetohydrodynamic
  simulations improve, these can provide valuable insight about the
  profile and the total energy of turbulence in clusters. This will
  further help us to distinguish the three different models from each
  other.} We will pursue further implications and distinguishing
characteristics of these competing models in future work.

>>>>

However, we assume a simplified and stationary model for magnetic
fields and turbulence. We do not account for the time-varying energy
density in compressible waves, which are thought to be necessary for
the acceleration process \citep{brunetti07,brunetti11}, as the cluster
merger proceeds.  So our approach is orthogonal (and complementary) to
e.g., simulations of \citealp{2015ApJ...800...60M} that focus on the
time-dependent compressible turbulence while adopting a simplified
treatment of CR that does not follow the transport of the CR
distribution function. Our approach of parametrizing turbulence
enables us to vary parameters associated with the unknown continuation
of magneto-hydrodynamical (MHD) turbulence below the MHD scale and the
overall amplitude of compressible waves (that can in principle vary
depending on the details of a particular cluster merger).

@@

In this setion, we solve the Fokker-Planck equation for CR transport
on Lagrangian particle trajectories through cosmic history.  We
concentrate on three scenarios. (i) In model {\em M-primaries}, we
assume that CR electrons, which have been accelerated by cosmic
formation shocks and successively cooled by inverse Compton and
synchrotron losses, form a fossil seed population for
reacceleration. (ii) In model {\em M-streaming}, we account for the
outward streaming of central CRps, which produces a flat CR
distribution in the ICM and equivalently a flat secondary seed
population of CRe for reacceleration. (iii) In model {\em
  M-turbulence} we adopt a spatially flatter turbulent profile than
what was adopted before but assume that seed CRps and secondary CRes
follow the steep profile that is suggested by structure formation
simulations.

The level of emission is mainly driven by how efficient the CRs are
reaccelerated and for how long. Hence, we exploit the exponential
sensitivity of reacceleration on the level of turbulence and adopt
different radial profiles of the turbulent energy density. We ask the
question how differently the turbulent profiles need to be shaped in
order to reproduce the observed radial profiles of the radio
emission. For these models, we then compute radio spectra and
gamma-ray luminosities and compare to observational data.

\subsection{Modelling diffusive shock acceleration}
\label{sec:cosmo_sim}
In this paper we focus on our simulated cluster, g72a, which is a
massive cluster of mass $M_{200}=1.6\times10^{15}\,M_\odot$ that
experienced a merger about 1 Gyr ago
\citep{2009MNRAS.399..497D}. Since the cluster mass, density and
temperature profiles are all similar to the well studied Coma cluster
\citep{2007MNRAS.378..385P,pinzke10}, we will compare our calculations
to radio and gamma-ray observations of Coma.

We use a simple test-particle model for the CR acceleration and
injection, where each shock injects CRs that trace a power-law in
momentum,
\begin{equation}
  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
\end{equation}
determined by the normalization $C(t)$ and the spectral index
$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
$\mathcal{M}$. It is given by the ratio of the upstream velocity
($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
energy density are derived from
\begin{eqnarray}
n_\rmn{p} &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
\eps_\rmn{p} &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
\end{eqnarray}
where $E(p) = (\sqrt{1+p^2} -1)\, m\,c^2$ is the kinetic energy of a
particle with momentum $p$. We adopt a fit to Monte Carlo simulations
of the thermal leakage process that relates the momentum of injected
protons ($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the
shocked plasma \citep{kang11}:
\begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} = x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
  \frac{1.07}{\epsilon_B}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
\end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which -- as we will later see -- corresponds to a conservative maximum
energy acceleration efficiency for protons of $10\%$. To derive the
acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{p,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\eps_\rmn{p,lin} =
  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
  \,\frac{\eps_\p}{n_\p}
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.

@@

In our Galaxy, the CRe-to-CRp ratio at a few GeV is $K_{\rmn{ep}} \sim
10^{-2}$. Hence, we adopt this as a fiducial value for the CRe-to-CRp
acceleration efficiency \citep[see][for more
  discussion]{pinzke13}. However, as recent PIC simulations have
shown, this is likely very different at weak shocks, with electrons
efficiently accelerated at perpendicular shocks
\citep{2014ApJ...794..153G,2014ApJ...797...47G}, and ions efficiently
accelerated at parallel shocks \citep{2014ApJ...783...91C}. Thus,
depending on magnetic geometry, $K_{\rmn{ep}}$ could be either larger
or smaller. Some observations of radio relics suggest high values of
$K_{\rmn{ep}}$, due to the absence of gamma-ray emission, which probes
the CRp population \citep{2014MNRAS.437.2291V}. This suggests primary
CRes as a viable alternative scenario to secondary CRes as seeds for
the giant RHs. In our {\em M-primaries} scenario, the injected
distribution of CRes is derived in the same way as for the CRps. Once
they have been accelerated to relativistic energies, injected
electrons and protons are indistinguishable. We therefore assume that
CRp and CRe have the same distribution function $f_\rmn{e}(p) =
K_\rmn{ep} f_\rmn{p}(p)$, with a different normalization (due to
differing acceleration efficiencies) $K_\rmn{ep}=0.1$ \citep[which is
  viable for primarily perpendicular
  shocks,][]{2014ApJ...794..153G}. While this appears to contradict the
radial bias of magnetic fields in the bulk of the ICM as suggested by
observations \citep{2010NatPh...6..520P} and cluster simulations
\citep{2011ApJ...740...81R}, it does not necessarily apply to the
accretion shock regions, which show a field geometry with a net
perpendicular bias with respect to the shock normal---at least for
giant radio relics \citep{2010Sci...330..347V}.

@@

In Fig.~\ref{fig:sync_profile}, we show radial profiles for the radio
emission in all three scenarios in which the seeds undergo Fermi-II
reacceleration in turbulent fields that are shaped such as to
reproduce the Coma RH profile at 352~MHz.  Adopting our
parametrisation for the volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, we find
$\alpha_\rmn{tu}= 0.67$ for \Mflatturb, $\alpha_\rmn{tu}= 0.82$ for
\Mstream, and $\alpha_\rmn{tu}= 0.88$ for \Mprimary. As a result, the
ratio of turbulent-to-thermal energy densities slightly increase with
radius as shown in Fig.~\ref{fig:turb}.  After turbulent
reacceleration, the volume-weighted, relative CRp energy density and
relative CRp number density inside the RH for \Mflatturb (\Mstream),
are found to be 2 (3) \% and $2\times10^{-8}$ ($5\times10^{-8}$),
respectively.

%the turbulent energy density becomes $\eps_\rmn{turb} \propto
%\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
%temperature of the gas,

@@

Figure~\ref{fig:sync_profile} demonstrates that the modeled radio
profiles without turbulent reacceleration are too steep.  In the
bottom right panel of Fig.~\ref{fig:sync_profile} (labeled with
Brunetti et al. 2012), we show that our simulated profiles of
reaccelerated CRs, which only take advective CR transport into
account, i.e. they neglect CR streaming or a flatter turbulent
profile, produce radio profiles that are too steep. Indeed, even using
the assumptions of previous work -- where complete freedom in the seed
population was allowed -- it is not possible to reproduce observations
in both frequencies in any model.\footnote{Note that in previous work
  on the Coma cluster, $\eps_\rmn{turb} \propto \eps_\rmn{th}$ was
  adopted which approximately corresponds to $\alpha_\rmn{tu}= 1$
  \citep{brunetti12} and together with the different distributions for
  seed CRes constitute the main differences compared to our work.}
Decreasing the acceleration efficiency with radius does not change
this conclusion much because of the weak radial dependence of
$D_\rmn{pp}(R)\propto \eps_\rmn{th}(R)^{\alpha_\rmn{tu}-1}
\sqrt{T(R)}$. This signals that the problem is generic and requires
either additional modifications to the plasma physics of acceleration
or a better understanding of potential observational systematics. In
addition there are differences in the simulated density and
temperature profiles in comparison to the observed profile in Coma
that impact the CR abundance as well as cooling and reacceleration.

@@

In principle, reacceleration via TTD leads to spectral steepening with
particle energy due to the inefficiency of the acceleration process to
counter the stronger cooling losses with increasing energy. Since
synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
spectral steepening of the radio spectrum (see the left panel of
Fig.~\ref{fig:sync_spectrum} where the continuous injection of
secondary CRes is absent). A given radio window samples higher energy
electrons for a decreasing field strength in the cluster
outskirts. Hence, the spectral steepening with energy should translate
into a radial spectral steepening \citep{brunetti12}. However, because
of the weak dependence of the electron Lorentz factor on emission
frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
importantly, our simulated fluid elements at a given radius sample a
broad distribution of shock history, density and temperature, which
implies very similar synchrotron brightness profiles at
$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
and simulated 1.4 GHz profiles could instead be due to systematic flux
calibration error in single dish observations. These could arise, for
instance, due to errors in point source subtraction. Interestingly, we
can match the 1.4 GHz data if we reduce the zero point by adding 10\%
of the central flux to every data point; this flattens the outer
profile\footnote{Lawrence Rudnick, private communication.}.
Alternatively, this may point to weaknesses in the theoretical
modeling of the particle acceleration process and may require a
stronger cutoff in the particle energy spectrum.

\subsection{Radio spectrum}
\label{sect:radio_spec}
In Fig.~\ref{fig:sync_spectrum} we show that our three models that
include Fermi-II reacceleration can individually reproduce the
convexly curved total radio spectrum found in the Coma cluster. Seed
CRs in \Mstream and \Mflatturb that do not experience turbulent
reacceleration have a power-law spectrum in disagreement with
observations. In order to match both the spatial and spectral profiles
in Coma, we adopt an acceleration efficiency for the strongest shocks
in our three models \Mprimary, \Mstream, and \Mflatturb to
$\zeta_{\rmn{e}} <0.003$, $\zeta_{\rmn{p}} < 0.1$, and
$\zeta_{\rmn{p}}<0.03$, respectively. Following the Mach number
($\mathcal{M}$)-dependence of the acceleration efficiency suggested in
\cite{pinzke13}, the efficiency in weak shocks ($\mathcal{M}\sim
2.5-3.5$) that dominates the CR distribution function, has an
acceleration efficiency for protons $\zeta_{\rmn{p}}\sim0.0001-0.01$,
and for electrons $\zeta_{\rmn{e}}\sim 0.001$.

Interestingly, we find that the radio luminosity from clusters in the
OFF-state (DSA only) and ON-state (DSA and reacceleration) differ by
about a factor 10-20 in all our three models. This means that the
secondary CRes are dominated by the reaccelerated fossil CRes and not
from the CRes produced by reaccelerated CRps. However, for high
frequencies ($\nu_\rmn{syn}\gtrsim$ GHz) where synchrotron cooling is
more efficient than reacceleration, the emission is dominated by the
CRes produced in the continuous injection of electrons from
reaccelerated CRps. It is also worth mentioning that the radio
emission from secondary CRes are smoothly distributed around the
cluster because of the continuous injection, hence the it is not
dominated by outliers.

However, for \Mprimary, the primary CRes that generate most of the
radio emission from the cluster in the OFF-state are dominated by only
a small fraction of the CRes. These electrons are injected very
recently and have not had time to cool yet. Hence we expect there to
be a large variance in the OFF-state of different simulated
clusters. As mentioned in section~\ref{sect:param_comp}, combining
radio observations with gamma-ray limits allows us to put a lower
limit to $X_\rmn{tu}$.  If $X_\rmn{tu}$ is smaller than in our adopted
models (where we assume $X_\rmn{tu}=0.2$), then the efficiency of DSA
has to be larger than $\zeta_\rmn{p}\sim 0.1$ for the secondary CRes
to reproduce the radio observations. However, since the turbulent
reacceleration acts on both the secondary CRes and the CRps, while
$\zeta_\rmn{p}$ only affects the CRps, \Mstream and \Mflatturb would
produce too much gamma-rays. Hence we conclude that
$X_\rmn{tu}\gtrsim0.2$ if all other parameters are kept
fixed. Although, we caution the reader to take this limit too
stringent because of the uncertainty in $k_0$ and $\tau_\rmn{cl}$ that
impact $X_\rmn{tu}$ for a fixed $\tau_\rmn{D}$. This parameter space
needs to be explored further in future work in order to put more
stringent limits on the level of turbulence in clusters using radio
and gamma-ray observations in combination with turbulent reaccelerated
CRs.

@@

How could we distinguish the different possibilities of a dominating
primary or secondary seed population of electrons observationally?
One possibility that is relative insensitive to adopted parameters in
our models is to use high-frequency radio observations (with e.g., the
Jansky Very Large Array) where turbulent reacceleration of CRes (which
has a high energy cutoff) is no longer efficient since their fast
radiative cooling time drops below the comparably slow reacceleration
timescale producing a sharp spectral cutoff. This is unlike
reacceleration of CRps that do not suffer radiative cooling losses and
inject power-law momentum distributions of secondary CRe (see
Fig.~\ref{fig:sync_spectrum}).

However, the negative flux bowl of the Sunyaev-Zel'dovich effect
introduces a cutoff of the RH spectrum at frequencies above $\gtrsim
10$~GHz \citep[][ depending on cluster mass and
  redshift]{2002A&A...396L..17E,Pfrommer:2003mk}. Hence the
subdominant radio emission from freshly injected secondary CRes may
only be detectable in steep spectrum radio sources
\citep{2008Natur.455..944B}, which exhibit a cutoff at lower radio
frequencies and are thought to represent dying RHs as a result of the
decaying turbulence after a merger. Alternatively, one could attempt
to reconstruct the intrinsic high-frequency RH spectrum by filling in
the missing flux due to the Sunyaev-Zel'dovich effect by precise
measurements of the Compton-$y$ parameter at microwave
frequencies. Another possibility would consist in stacking the radio
data of radio-quiet clusters that do not exhibit RH emission
individually \citep{2011ApJ...740L..28B}. This may reveal the
glow of radio emission due to steady state secondary
population. Emission from faint secondary electrons should still be
visible, whereas due to the much more intermittent nature of DSA
injection, primary CRe will instead show a sharp cutoff due to
cooling, and will not be visible at high energies (see
Fig.~\ref{fig:sync_spectrum}).

As MHD simulations of clusters that follow spectral CR distributions
become feasible, these will provide valuable insight about the profile
and the total energy of turbulence in clusters and the possibility of
turbulent reacceleration. This will further help us to distinguish the
three different models from each other. We will pursue further
implications and distinguishing characteristics of these competing
models in future work.
